Optimizing Pypy's Garbage Collector for Copy On Write Performance given a forky Web-Server Workload

### 2018-03-01 paper/main.tex
Wrote related work section

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}
\titleformat*{\subsubsection}{\normalsize\bfseries}
\titleformat*{\paragraph}{\normalsize\bfseries}
\titleformat*{\subparagraph}{\normalsize\bfseries}

@@

\section{Methodologies}
\begin{enumerate}
  \item Ngnx + uWSGI + Django + pypy in multi-process mode
  \item Pick some website that uses a lot of memory... thebluealliance.com is open source and operates on django and caches a lot of info locally
  \item Generate a bunch of fake traffic 
  \item Monitor running code
  \begin{enumerate}
  	\item Total memory of all processes
    \item Average memory of each process
    \item shared memory per process
    \item num page faults
    \item cache miss rate?
    \item pages served per second (did it go up or down?)
    \item How many times did major and minor garbage collection happen?
    \item How many times did this inter-generation optimization actually occur?
  \end{enumerate}
\end{enumerate}

@@

\section{Related work}
\begin{enumerate}
  \item Ruby's Copy-On-Write optimized mark-and-sweep garbage collector
  \item Instagram's CPython patch for python's mark-and-sweep garbage collector
\end{enumerate}

>>>>

%\usepackage{titlesec}

%\titleformat*{\section}{\normalsize\bfseries}
%\titleformat*{\subsection}{\normalsize\bfseries}
%\titleformat*{\subsubsection}{\normalsize\bfseries}
%\titleformat*{\paragraph}{\normalsize\bfseries}
%\titleformat*{\subparagraph}{\normalsize\bfseries}

@@

  \section{Methodologies}
  \begin{enumerate}
	\item Ngnx + uWSGI + Django + pypy in multi-process mode
	\item Use thebluealliance.com as a test load becaues it caches a lot of data and does some non-trivial computation
	\item Generate a bunch of fake traffic using httperf
	\item Monitor running code
	  \begin{enumerate}
        \item How long did it take to handle 10,000 requests
        \item What was the average time-to-last-byte?
		\item Total memory of all processes
		\item Average memory of each process
		\item shared memory per process
		\item num page faults
		\item cache miss rate?
		\item pages served per second (did it go up or down?)
		\item How many times did major and minor garbage collection happen?
		\item How many times did this inter-generation optimization actually occur?
	  \end{enumerate}
  \end{enumerate}

@@

  \section{Related work}

  This paper is very much inspired by recent updates in CPython's and Ruby MRI's garbage collectors which were updated in 2017 and 2014 respectively.

  \subsection{Copy-On-Write optimization in Ruby MRI's MSGC}
  Ruby 2.0 contains an update to the GC that improved CoW performance.  Ruby's GC is a classic CGGC with a young generation and an old generation.  In the old algorithm, every object contained a "visited" bit that would note whether the object had visited by the tracer.  In the new GC algorithm, these "visited" bits are stored outside the objects being traced.  In this way, the objects themselves don't need to be updated during a GC event.

  The optimization described in this paper is different in that we focus on preserving old objects when objects are copied from eden into the older generation.

  \subsection{Copy-On-Write Friendly Garbage Collection in CPython at Instagram}
  A 2017 article from Instagram's Engineering series describes changes to CPython's garbage collector made at instagram aimed at improving memory performance in their web-tier servers.  The experimentation section of this paper is heavily inspired by the test setup used at Instagram.

  The optimization implemented at instagram was to have the programmer manually mark certain objects as "GC-Frozen".  Objects that are GC-Frozen are not touched by the garbage collector and so the data in and around them is not touched.  Because Instagram's specific use case involves a lot of static objects that are shared between processes, this worked effectively.
